High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-05-31 paper/main.tex
updates to higher order sim text

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/higher_order_sims}
  \caption{\textbf{Recovery of simulated first-order and second-order dynamic correlations.}  Each panel displays the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices at each
    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
    randomly generated synthetic datasets of the given category.)
    Error ribbons denote 95\% confidence intervals (taken across
    datasets).  For a complete description of each synthetic dataset,
    see \textit{Synthetic data: simulating dynamic higher-order
      correlations}.  All estimates represented in this figure were
    computed using a Laplace kernel
    (width~$=20$).  \textbf{a. Constant correlations.}  These datasets
    have stable (unchanging) underlying second-order correlation
    matrices.  \textbf{b. Random correlations.} These datasets are
    generated using a new independently drawn second-order correlation
    matrix at each timepoint.  \textbf{c. Ramping correlations.}
    These datasets are generated by smoothly varying the underlying
    second-order correlations between the randomly drawn correlation
    matrices at the first and last timepoints.  \textbf{d. Event-based
      correlations.}  These datasets are each generated using five
    randomly drawn second-order correlation matrices that each remain
    stable for a fifth of the total timecourse.  The
    vertical lines denote event boundaries.}
  \label{fig:higher_order_sims}
\end{figure}

@@

The central mathematical operations in our procedure are two bookkeeping
functions, $\mathrm{vec}(\cdot)$ and $\mathrm{mat}(\cdot)$.  The
$\mathrm{vec}(\cdot)$ function takes as input a $K \times K$ symmetric
matrix and returns as output a
$\left(\frac{K^2 - K}{2} + K\right)$-dimensional column vector
containing the entries in the upper triangle and diagonal.  The
$\mathrm{mat}(\cdot)$ function inverts $\mathrm{vec}(\cdot)$ by taking
as input a $\left(\frac{K^2 - K}{2} + K\right)$-dimensional column
vector and returning a $K \times K$ symmetric matrix as output.  We
can then generate an order $n$ correlation matrix (for one timepoint, $t$) from an order
$n - 1$ template (from the same timepoint) as follows:
\begin{align}
  \mathbf{\Sigma_{n}}(t) &= \mathrm{mat}(\mathrm{vec}(\mathbf{\Sigma_{n-1}}(t)) \otimes \mathrm{vec}(\mathbf{\Sigma_{n-1}}(t))^\top).\label{eqn:veccorr}
\end{align}

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/higher_order_sims}
  \caption{\textbf{Recovery of simulated first-order and second-order dynamic correlations.}  Each panel displays the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices at each
    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
    randomly generated synthetic datasets of the given category.)
    Error ribbons denote 95\% confidence intervals (taken across
    datasets).  For a complete description of each synthetic dataset,
    see \textit{Synthetic data: simulating dynamic higher-order
      correlations}.  All estimates represented in this figure were
    computed using a Laplace kernel
    (width~$=20$).  \textbf{Constant correlations.}  These datasets
    have stable (unchanging) underlying second-order correlation
    matrices.  \textbf{Random correlations.} These datasets are
    generated using a new independently drawn second-order correlation
    matrix at each timepoint.  \textbf{Ramping correlations.}
    These datasets are generated by smoothly varying the underlying
    second-order correlations between the randomly drawn correlation
    matrices at the first and last timepoints.  \textbf{Event-based
      correlations.}  These datasets are each generated using five
    randomly drawn second-order correlation matrices that each remain
    stable for a fifth of the total timecourse.  The
    vertical lines denote event boundaries.}
  \label{fig:higher_order_sims}
\end{figure}

@@

The central mathematical operations in our procedure are two bookkeeping
functions, $\mathrm{vec}(\cdot)$ and $\mathrm{mat}(\cdot)$.  The
$\mathrm{vec}(\cdot)$ function takes as input a $K \times K$ symmetric
matrix and returns as output a
$\left(\frac{K^2 - K}{2} + K\right)$-dimensional column vector
containing the entries in the upper triangle and diagonal.  The
$\mathrm{mat}(\cdot)$ function inverts $\mathrm{vec}(\cdot)$ by taking
as input a $\left(\frac{K^2 - K}{2} + K\right)$-dimensional column
vector and returning a $K \times K$ symmetric matrix as output.  We
can then generate an order $n$ correlation matrix (for one timepoint, $t$) from an order
$n - 1$ template (from the same timepoint) using the Kronecker product as follows:
\begin{align}
  \mathbf{\Sigma_{n}}(t) &= \mathrm{mat}(\mathrm{vec}(\mathbf{\Sigma_{n-1}}(t)) \otimes \mathrm{vec}(\mathbf{\Sigma_{n-1}}(t))).\label{eqn:veccorr}
\end{align}
